---
title: "Summary Statistics"
output:
  html_document:
    toc: yes
  html_notebook:
    self_contained: yes
    toc: yes
---


```{r setup, include=FALSE}
library(pacman)  # You must install pacman if not already installed
                 # after that the other libraries will install if needed
p_load(ggplot2)
p_load(dplyr)
p_load(Hmisc)
p_load(magrittr)
p_load(tidyr)
p_load(scales)
p_load(htmlwidgets)
p_load(formattable)
p_load(plotly)
```

```{r load_data, include=FALSE}
# We will get the data using the eboxr package
pacman::p_load(eboxr)
attributes <- eboxr_read("/Users/curtbergmann/Box Sync/Elicit Education/scholar/summary_statistics/attributes.RDS",
           read_fun = readRDS)
options(scipen=9)
```


The homework assignment is to explore a variable in the attributes dataset. I will look at two year
redemptions.

```{r describe}
describe(attributes$num_redemptions_2yr)
```

There are cases with '?' as a value. In case of redemptions it's likely that customers with missing values have never redeemed a flight, so I'll convert these cases to 0. 

```{r fix missing}
attributes_clean <- attributes %>% 
  mutate(num_redemptions_2yr = as.numeric(ifelse(num_redemptions_2yr=='?',0,num_redemptions_2yr)))

describe(attributes_clean$num_redemptions_2yr)
```

These are likely customers who don't have a loyalty account and so can't redeem. Let's check that out

```{r loylaty}
attributes_clean %>% 
  group_by(loyalty_status) %>% 
  summarise(min = min(num_redemptions_2yr)
            , median = median(num_redemptions_2yr)
            , mean = mean(num_redemptions_2yr)
            , n = n()) %>% 
  mutate(pct = n / sum(n))
```

My suspicion is confirmed. Non-members have never redeemed a flight, and these customers make up 43% of the population.  

Let's look at the overall distribution of this variale
```{r hist}
ggplot(attributes_clean, aes(num_redemptions_2yr)) +
  geom_histogram()
```

The vast majority of customers have never redeemed a flight in the past two years. So next I'll just look at customer who have redeemed

```{r hist2}
ggplot(attributes_clean %>% filter(num_redemptions_2yr>0), aes(num_redemptions_2yr)) +
  geom_histogram()
```

Even in this scenario the distribution is very right skewed.

Next I'll look at how these distributions vary by loyalty_status, first getting the data into a tidy form that's easier to analyze and plot
```{r tidy}
attributes_tidy <- attributes_clean %>% 
  select(fake_id, SEGMENT_ASSIGNED, loyalty_status, num_redemptions_2yr) %>% 
  gather(attribute, value, -fake_id, -SEGMENT_ASSIGNED, -loyalty_status)
```

```{r facet}
attributes_tidy %>% 
  ggplot(aes(value)) %+% 
  geom_histogram() %+%
  facet_wrap(~loyalty_status, scales = "free")
```

We see that all non-members have never redeemed and that the skewness of the redeemption distribution declines as we move from the general populatoin "rr member" to the most frequent travelers "a-list prefered"

Let's look at the same view by segment
```{r facet_segment}
attributes_tidy %>% 
  ggplot(aes(value)) +
  geom_histogram() +
  facet_wrap(~SEGMENT_ASSIGNED, scales = "free")
```

Segment 1 has much higher redeemption frequency. Let's look at the quantiles by segment 

```{r quantiles}
attributes_tidy %>% 
  group_by(SEGMENT_ASSIGNED) %>% 
  summarise(quantiles = paste(round(quantile(value, c(0.01, 0.05, 0.5, 0.95, 0.99), na.rm=TRUE), 2), collapse=",")
            , n = n()
            , redemptions = sum(value)) %>%
  ungroup() %>% 
  mutate(pct_redemptions = redemptions / sum(redemptions)) %>% 
  extract(quantiles, c("q01", "q05", "q50", "q95", "q99")
          , regex = "(\\d+\\.?\\d*),(\\d+\\.?\\d*),(\\d+\\.?\\d*),(\\d+\\.?\\d*),(\\d+\\.?\\d*)")
```

Segment one is a small portion of shoppers but makes up 64% of all redemptions. Even the lowest quantiles of segment one have redeemed points in the last two years.
